Uncertainty on the galaxy-halo connection for Lyman-$\alpha$ emitters at $z=3.1$

### 2016-06-14 paper/ms.tex
full reply ready, new references

In this paper we investigate the impact of cosmic variance in
constraining the mass and occupation fraction of halos hosting LAEs at $z=3$.
We build mock surveys from a cosmological N-body simulation to compare them
against the observations of \cite{Bielby16} using the angular
correlation function.  
We use a simple model to populate a halo in the simulation with a LAE   
assuming a minimum, \mmin, and maximum mass, \mmax, for the dark
matter halos hosting LAEs.  We do not  assume  an underlying relation 
between the \ly\  luminosity and the dark matter halo mass.  
This approach bypasses all the physical uncertainties associated to
star formation and radiative transfer. 
We then use the Markov Chain Monte Carlo technique to obtain the
likelihood of the parameters given the observational constraints.
This approach allows us to estimate cosmic variance directly from
simulations without making any assumption  on the correlation function
behavior. ma

@@

We chose this simulation based on three requirements. 
First, the simulation should have cosmological parameters consistent
with the most recent constraints from Cosmic Microwave Background
experiments and provide public acces to the data.
Second, the halo mass function from the simulation should be robust
down to masses that include the range of possibilities from previous
observational efforts \cite[e.g. results from][impose a lower bound of
  $10^{10}$\hMsun.]{Hayashino2004,Gawiser2007,Ouchi2010,Bielby16} .
Third, the total volume of the simulation should be at least 10 times
larger the equivalent volume of a single LAE observation field.
These conditions are met as we describe below.

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.85\textwidth]{fig3.pdf}
\end{center}
\caption{One and two dimensional projections of the posterior
  probability distributions of \mmin, \mmax\ and \focc. 
  The models with $\log \focc>0.00$ ($\focc>1$) correspond  to models
  where the number density  of halos is smaller than the number of
  observed LAEs but we consider them as consistent because of the uncertainty
  in the median number density due to cosmic variance. See 
Fig. \ref{fig:cosmicv0} and \S\ref{subsec:explore} for details.} 
\label{fig:like}
\end{figure*}

@@

\bibliographystyle{apj}
%\bibliography{references.bib}

\begin{thebibliography}{39}
\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi

@@

\bibitem[{{Jose} {et~al.}(2013){Jose}, {Srianand}, \&
  {Subramanian}}]{Jose2013b}
{Jose}, C., {Srianand}, R., \& {Subramanian}, K. 2013, ArXiv e-prints

\bibitem[{{Klypin} {et~al.}(2014){Klypin}, {Yepes}, {Gottlober}, {Prada}, \&
  {Hess}}]{BolshoiP}
{Klypin}, A., {Yepes}, G., {Gottlober}, S., {Prada}, F., \& {Hess}, S. 2014,
  ArXiv e-prints

@@

\bibitem[{{Somerville} {et~al.}(2004){Somerville}, {Lee}, {Ferguson}, {Gardner},
  {Moustakas}, \& {Giavalisco}}]{Somerville2004}
{Somerville}, R.~S., {Lee}, K., {Ferguson}, H.~C.,
	{Gardner}, J.~P., {Moustakas}, L.~A., \& {Giavalisco}, M. 204, \apj,
  600, 171

>>>>

In this paper we investigate the impact of cosmic variance in
constraining the mass and occupation fraction of halos hosting LAEs at $z=3$.
We build mock surveys from a cosmological N-body simulation to compare them
against the observations of \cite{Bielby16} using the angular
correlation function.  
We use a simple model to populate a halo in the simulation with a LAE   
assuming a minimum, \mmin, and maximum mass, \mmax, for the dark
matter halos hosting LAEs.  We do not  assume  an underlying relation 
between the \ly\  luminosity and the dark matter halo mass.  
This approach bypasses all the physical uncertainties associated to
star formation and radiative transfer. 
We then use the Markov Chain Monte Carlo technique to obtain the
likelihood of the parameters given the observational constraints.
This approach allows us to estimate cosmic variance directly from
simulations without making any assumption  on the correlation function
behavior.

@@

We chose this simulation based on three requirements. 
First, the simulation has cosmological parameters consistent
with the most recent constraints from Cosmic Microwave Background
experiments and provide public acces to the data.
Second, the halo mass function from the simulation is robust
down to  $10^{10}$\hMsun, which is the lower halo mass bound suggested
by previous observational 
studies\citep{Hayashino2004,Gawiser2007,Ouchi2010,Bielby16}. 
Third, the total volume of the simulation is at least 10 times
larger the equivalent volume of a single LAE observation field.
These conditions are met as we describe below.

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.85\textwidth]{fig3.pdf}
\end{center}
\caption{One and two dimensional projections of the posterior
  probability distributions of \mmin, \mmax\ and \focc. 
  Vertical lines in the one dimensional proyections correspond to the
  14-50,84 percentiles of the distribtions.
  Thick lines in the two dimensional planes mark the 1-2-3 $\sigma$
  contours of the corresponding joint distributions.
  The models with $\log \focc>0.00$ ($\focc>1$) correspond  to models
  where the number density  of halos is smaller than the number of
  observed LAEs but we consider them as consistent because of the uncertainty
  in the median number density due to cosmic variance. See 
Fig. \ref{fig:cosmicv0} and \S\ref{subsec:explore} for details.} 
\label{fig:like}
\end{figure*}

@@

\bibliographystyle{apj}
%\bibliography{references.bib}
\begin{thebibliography}{43}
\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi

@@

\bibitem[{{Jose} {et~al.}(2013){Jose}, {Srianand}, \&
  {Subramanian}}]{Jose2013b}
{Jose}, C., {Srianand}, R., \& {Subramanian}, K. 2013, \mnras, 435, 368

\bibitem[{{Klypin} {et~al.}(2016){Klypin}, {Yepes}, {Gottl{\"o}ber}, {Prada},
  \& {He{\ss}}}]{BolshoiP}
{Klypin}, A., {Yepes}, G., {Gottl{\"o}ber}, S., {Prada}, F., \& {He{\ss}}, S.
  2016, \mnras, 457, 4340

@@

\bibitem[{{Somerville} {et~al.}(2004){Somerville}, {Lee}, {Ferguson},
  {Gardner}, {Moustakas}, \& {Giavalisco}}]{Somerville2004}
{Somerville}, R.~S., {Lee}, K., {Ferguson}, H.~C., {Gardner}, J.~P.,
  {Moustakas}, L.~A., \& {Giavalisco}, M. 2004, \apjl, 600, L171
